---
title: "Introduction to FLAME"
author: "Vittorio Orlandi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to FLAME}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Overview
FLAME (Fast, Large-scale Almost Matching Exactly) is a fast, interpretable matching method for causal inference. It matches units via a learned, weighted Hamming distance that determines what covariates are more important to match on. 

We can start by loading FLAME...
```{r setup}
devtools::load_all()
```

... and generating some toy data:
```{r}
set.seed(44)
data <- gen_data() # Data we would like to match
holdout <- gen_data() # Data we will train on, to compute PE 
```


To run FLAME with its default settings:
```{r}
FLAME_out <- FLAME_bit_new(data = data, holdout = holdout)
```

By default, `FLAME` returns a list with *6* entries:
```{r}
names(FLAME_out)
```

The first, `FLAME_out$data` contains the original data frame with two modifications:

1. There is an extra logical column, `FLAME_out$data$matched`, that indicates whether or not the corresponding unit was matched. This can be useful if you'd like to use only the matched data for subsequent analysis:
```{r}
matched_data <- dplyr::filter(FLAME_out$data, matched)
```

2. Units that were matched, but not on all covariates, will have a \* in place of their covariate value for all covariates for which they were not matched. 
```{r}
head(FLAME_out$data)
```
The above, for example, implies that while unit 1 was matched to units that also had values (X1, X2, X3, X4, X5) = (1, 1, 0, 0, 0), unit 3 was matched to units that shared values of (X2, X3) = (1, 0), but that differed in their values of X1, X4, and X5. Units 3 and 4 were not matched at all.

The second, `MGs` is a list, each entry of which contains the units in a single matched group. 
```{r}
FLAME_out$MGs[[1]]
length(FLAME_out$MGs)
```
That is, units 1, 15, 23, and 41 were all matched together and there are 13 matched groups total. 

The third, `CATE`, complements `MGs` by supplying the CATE for each matched group. For example, the CATE for the matched group above, of units 1, 15, 23, and 41, is given by:
```{r}
FLAME_out$CATE[1]
```

The fourth, `matched_on`, is a list also corresponding to `MGs` that gives the covariates, and their values, on which units in each matched group were matched. 
```{r}
FLAME_out$matched_on[[1]]
```
The above shows that each of the units in the first matched group had covariate values (X1, X2, X3, X4, X5) = (1, 1, 0, 0, 0). For matched groups not formed on all covariates, some of these entries will be missing:
```{r}
FLAME_out$matched_on[[7]]
```
Thus, the units in the seventh matched group, as defined by `MGs[[7]]`, shared the same values of X1, X2, X3, and X4, but not of X5. 

The fifth, `matching_covs` is a list, which shows the covariates that were used to match on every iteration of FLAME:
```{r}
FLAME_out$matching_covs
```
Thus, first, some units were matched on covariates X1, X2, X3, X4, X5. Then, more units were matched on all covariates but X5, and so on. 

The sixth, `dropped` describes the order in which covariates were dropped:
```{r}
FLAME_out$dropped
```
Thus, first covariate X5 was dropped, then X4, and so on. This information is directly inferrable from `matching_covs`, but for large numbers of covariates, `dropped` provides an easier way of identifying the order in which covariates were dropped. 


# Post-Matching Analysis
After `FLAME` has been run, the matched data can be used for a variety of purposes. The FLAME package provides functionality for a few quick, post-matching analyses, via the functions `CATE`, `ATE`, `ATT`, and `MG`.

`CATE(units, flame_obj)` takes in `units`, the units for which you would like an estimate of the conditional treatment effect, and the output of a run of FLAME, `flame_obj`. Note that you may supply only a single unit for the `units` argument and that the units will be indexed _with respect to the original data frame passed to_ `FLAME`. That is, values outside of [1, `nrow(flame_obj$data)`] will cause an error.

In this way, we can find the treatment effect for a unit of interest, say, unit 5...
```{r,eval=FALSE}
CATE(units = 5, flame_obj = FLAME_out)
```

... or for a class of units for which the treatment effect is of particular interest:
```{r,eval=FALSE}
CATE(units = which(data$age < 30 & data$treated == 1), flame_obj = FLAME_out)
```

`ATE(flame_obj)` and `ATT(flame_obj)` return the estimated average treatment effect and the estimated average treatment effect on the treated, respectively. 
```{r,eval=FALSE}
ATE(flame_obj = FLAME_out)
ATT(flame_obj = FLAME_out)
```

Lastly, we can use `MG(units, flame_obj)` to get a list of the members of the matched groups of all units in `units`:
```{r, eval = FALSE}
MG(units = 5, flame_obj = FLAME_out)
MG(units = which(data$age < 30 & data$treated == 1), flame_obj = FLAME_out)
```


